Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-05 inst/examples/20160715-slides-Krakow.Rmd
ok

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")

@@

```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=6, fig.height=5, fig.show="hold", out.width="150px"}
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingactivitycomparisons-2.png
selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) # %>%
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = spread(df2, publication_decade, n, fill = 0)
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {

>>>>

knitr::opts_chunk$set(echo = FALSE)
#knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/", dev="CairoPNG")
knitr::opts_chunk$set(fig.path = "slides_201606_Krakow/")

@@

```{r publishingactivitycomparisons, echo=FALSE, message=FALSE, cache=FALSE, fig.width=6, fig.height=5, fig.show="hold", out.width="150px"}
#https://github.com/rOpenGov/fennica/blob/master/inst/examples/figure_201606_Krakow/publishingactivitycomparisons-2.png

selected.places = c("Turku", "Uppsala", "Lund", "Stockholm")
df2 <- df0 %>% group_by(publication_decade, publication_place, catalog) %>%
               summarise(n = n()) %>%
	       filter(publication_place %in% selected.places) 
df2$catalog = factor(df2$catalog, levels = rev(c("Fennica", "Kungliga")))
df2$publication_place = droplevels(factor(df2$publication_place))
df3 = spread(df2, publication_decade, n, fill = 0)
df2 = melt(df3)
colnames(df2) = c("publication_place", "catalog", "publication_decade", "n")
df2$publication_decade = as.numeric(as.character(df2$publication_decade))
df2$n = as.numeric(as.character(df2$n))
for (catal in unique(df2$catalog)) {
